On a Alvenicity of solar wind discontinuities

### 2024-08-14 article.qmd
update figures

@@

@@

- @steinhauerMultifluidModelOnedimensional2008

>>>>

Observations of magnetic discontinuities exhibit Alfvenic properties, with the plasma velocity variation correlating well with magnetic field components variations. However, the amplitude of the plasma velocity jump is often significantly smaller than the Alfvén velocity jump, indicating a more complicated picture than the classical MHD model of rotational discontinuities. @fig-examples show observations of  magnetic discontinuities in different regions of the heliosphere, PSP within 0.2 AU, Wind upstream of the Earth's bow shock, and ARTEMIS in the Earth's magnetotail. These differences could not be simply explained by the aniostropy of the plasma thermal pressure alone and suggest that kinetic mechanisms are necessary to describe the stress balance within discontinuities.

::: {.column-page}
::: {#fig-examples layout-nrow="1" }

![]()

Three examples of solar wind discontinuities observed by Parker Solar Probe (PSP), Wind and ARTEMIS spacecraft.

@@

::: {#fig-vRatioStats}
![](https://raw.githubusercontent.com/Beforerr/psp_conjunction/5e09973ebedbdaef5cc89cb3a12be3fb77f44570/figures/enc7/vl_ratio.png)

Statistics of the asymptotic velocity ratio from PSP, Wind, and ARTEMIS spacecraft observations during PSP encounter 7 period from 2021-01-14 to 2021-01-21.
:::

@@

- @steinhauerMultifluidModelOnedimensional2008
- @artemyevIonNongyrotropySolar2020
